Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2014-02-02 unstructured.tex
2013.10.20 (Alex) Text reworked and reviewed for introduction and unstructured sections. BibTeX file reformed and debugged (once more :-)

The key objective of the {\sl Gia} system~\cite{CRBLS2003} is 
to help alleviate the scalability omnipresent
in unstructured \p\ file-sharing systems.
At first, {\sl Gia} replaced {\sl Gnutella}'s blind flooding 
with random walks.
Although this adoption was 
a step in the right direction \cite{LCCLS2002},
issuing a single copy of the query within the network
effectively reduces the search scope and may negatively affect 
the success rate of the query in question.
To overcome this limitation, {\sl Gia} introduces
a token-based flow control mechanism 
that gradually redirects queries to nodes which are more
likely to answer. This flow control mechanism also helps prevent node
overloading as each peer ``announces'' the number of query requests it 
can handle, in terms of tokens, to its neighbors; to this end, 
peers only forward query requests to nodes that they previously
received tokens from. Further refinement to the search mechanism is the
support for \emph{one--hop replication} of pointers to content.
{\sl Gia} also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc., of \p\ nodes and uses this
information when connecting nodes to each other.
By using a topology adaptation algorithm, 
{\sl Gia} places low capacity nodes within 
short proximity to peers with high performance features.
This topology adaptation algorithm is based on the metric 
each node maintains about its satisfaction --ranging between $0$ and $1$--
for the neighbors it finds itself associated with. 
Through message exchange, a peer can establish new connections 
or drop superseded ones in order to improve its satisfaction.
Despite the fact that {\sl Gia}'s topology adaptation algorithm 
that primarily focuses on the satisfaction of peers improves the network's 
scalability it falls short in addressing the mismatch problem
as considerations for the underlying network are not handled in explicit
terms \cite{LXLNZ2005}. Moreover it reduces the search scope, exhibits poor
performance in the worst case when matching data is not found quickly
\cite{PR2004,HJ2004} and can potentially build  disconnected topoloagies
\cite{MBL2006}.
%
In terms of the $3$ stated criteria, {\sl Gia}'s approach is as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Reduces the search scope.
medium &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
Another problem with topology unaware
systems is the duplication of messages due to cycles in the network graph.
Interestingly, such cycles appear even along the correct forwarding path.
\cite{ZKB2008} focuses on this exact deficiency of overlay networks and
introduces the \emph{Distributed Cycle Minimization Protocol
(DCMP)}, a dynamic, fully distributed method that removes cycles;
this is accomplished without sacrificing
overlay connectivity, resilience and other key properties of unstructured
\p\ architectures and by avoiding a hierarchical organization of peers. 
Once a cycle is detected in {\it DCMP}, the most powerful node in that cycle 
is elected as the \emph{Gate Peer} and the cycle is then broken in that place
that it will result in the minimization of the distance between the
\emph{Gate Peer} and all other nodes that are currently part of the cycle. 
This process is managed by using two specialized message types 
namely, \emph{Information Collection Message (ICM)} and \emph{Cut Message (CM)}. 
\emph{DCMP} bases its operation on messages whose travel is limited by an
imposed $TTL$ value (max set to $7$ for most cases). This inherently limits
the protocol in detecting cycles that span for more than $TTL$ nodes.
Even though cycle elimination does improve network performance, 
it cannot  directly contribute to the solution of the topology mismatch
problem, while its perfomance in a high traffic and churn environments and its
ability to retain important characteristics of a Gnutella-like topology (i.e.,
like degree distribution, average peer distance, diameter e.t.c.) has been
doubted \cite{SCG2009,CSG2010}. On the other hand, even though some of the overhead
saved by the dublicate message reduction is spent to control the cycle cutting
mechanism it is reported that still stays for example one to two orders of
magnitude less than LTM due to its ``lazy'' broadcasting of control messages
(as opposed to LTM's periodic approach) \cite{ZKB2008}.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
% TODO: SOME DISCUSSION
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
The expected \emph{DCMP} behavior as far as our $3$ criteria is:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It returns more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimizes this as possible.
low &
% fully distributed method
high
\end{tabular}
}
\end{center}

@@

In \cite{LCCLS2002}, a \emph{k-walker} query algorithm is presented and shown
that using it along side square-root allocation results in perfomance similar to
Gnutella's query flooding method but incurring up to two
orders of magnitude less network traffic. Also checks $3$ strategies for
replica placement, namely \emph{owner replication} where an object is replicated
at the requesting node, \emph{path replication} that caches the object along the
path from the requesting to the providing node and \emph{random replication}
where the replication is taking place randomly on visited nodes. Observations in
this work are not directly applicable to structured DHTs, because it is assumed
that the lookup time for an object depends only on the number of replicas and
not the placement strategy \cite{RS2004}.

@@

%In \emph{Adaptive Connection Establishment (ACE)} \cite{LZXN2004}, the
%authors extend the idea of AOTO by introducing optimizations based on the
%depths of the minimum spanning trees. But since the network delay is not
%always a reliable estimation method to detect the physical location of peers,
%the algorithm still suffers from the discrepancies caused by mis-located nodes.
%%
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% compared to LTM it has slow convergence speed because of the information
% exchange among each peer and all its neighbours.
medium &
% A little bit better that AOTO since the computation here is done within a
% certain diameter from the source peer
medium &
% Larger diameter topologies lead to better topology optimization
% rate but also to higher communication and computation overhead.
medium
\end{tabular}
}
\end{center}

@@

The \emph{piggybacking component} requires peers 
to probe immediate neighbors using delay distance measurements 
and store information locally. The algorithm introduces a special query message
type, the \emph{Piggy Message (PM)} which includes information about 
the neighbor identification (IP) and measured distance ($d$). PMs are
piggybacked to normal
Gnutella messages. When node $P$ receives a query from $Q$ it constructs a
$PM_{PQ}$, piggybacks it to the query and forwards it to $P$'s neighbors. When
the neighbors recieve it they detach the $PM_{PQ}$, record the distance
$d_{PQ}$ and process the query normaly. Selection of which incoming queries
should be piggybacked with a \emph{PM} is proposed by either
\emph{pure probability-based (PPB)} or \emph{new neighbor triggered (NNT)}
policies.

The \emph{neighbor comparison and selection} component defines that a peer $S$
probe all his $2$-hops away neighbors (a set denoted as $ N^2(S)$) not probed
thus far. Let $P$ be a $1$-hop distance neighbor of $S$, and $Q$ be a probed
peer by $S$. When $S$ receives a message piggybacked with a $PM_{PQ}$ we
identify the following cases.
\begin{itemize}
  \item If $Q$ is already a direct neighbor of $S$ then we check the distances
  $d_{SQ}$, $d_{SP}$ and $d_{PQ}$. If either $d_{SQ}$ or $d_{SP}$ is the longest, then the longest
  link will be put in a \emph{will-cut} list\footnote{A peer will not send or
  forward queries to connections in its will-cut list but will preserve them
  for some time in order not to effect ongoing response messages travelling the
  inverse path.}. If $d_{PQ}$ is the longest then nothing is done by $S$; being
  fully distributed, neighbor comparison and selection process, will have the
  oportunity to handle $PQ$ link when initiated by peers $P$ or $Q$.

  \item If $Q$ is strictly a $2$-hop neighbor of $S$ and have never probed $Q$
  in the past, stores distance $d_{SQ}$ and checks distances $d_{SQ}$, $d_{SP}$ and $d_{PQ}$.
  If $d_{SQ}$ is the longest, $S$ will not create link $SQ$. If $d_{SP}$ is the
  longest, $SQ$ will be created and $SP$ will be put into the will-cut list.
  If $PQ$ is the longest, links $SP$ and $SQ$ will be preserved expecting that
  $P$ or $Q$ will disconnect $PQ$ later.
\end{itemize}

@@

As seen above, the method is fully distributed and needs only minimum knowledge
of, at most, a $2$-hop distant peers. This makes it a good candidate for big
overlay networks. Also topology adaptation helps construct a well fit overlay
network with restect to the underlying one (at least with respect to network
distances). Morever will-cut list and distance cache (which stores already
probed peers) minimize the unnecessary messages for the network maintenance.
There are works in the literature though that critisize, through simulation
results, the algorithm's average broadcast delay and overlay improvement
guarantee \cite{HLY2010}.
These characteristics are depicted to the $3$ evaluation criteria we use in this
survey as follows:

\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% 
medium &
% trivial overhead compared to the query cost savings and its convergent speed
% is faster than minimum spanning tree approaches so less overall overhead cost.
low &
% completely distributed and needs no global knowledge,
high
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \emph{Hops Adaptive Neighbor Discovery (HAND)} algorithm~\cite{CLZHC2006}
uses a fully-distributed triple--hop adjustment strategy, applied to a network
graph $G$ in order to create an optimal graph $G^{*}$, free of the implications
of topology mismatch. This optimality is attained if all peer hop 
sequences $(v_1, v_2, \ldots, v_k)$ of $G$ exist in $G^{*}$ and are in the same
order. The latter indicates that in practice triple sequences $(v_1, v_2, v_3)$
are used. A mismatch is detected as follows: supposing that we want to verify
a sequence, say $v_2-v_1-v_3$, two probing messages are dispatched from $v_1$ to
$v_2$ and $v_3$ and yield delays of $x$ and $z$ respectively.
%
When the probing message arrives at $v_2$, it gets forwarded
directly to $v_3$. 
Similarly, the message reaching $v_3$, it is directly forwarded to $v_2$.
The above two forwarding actions seek to quantify 
the corresponding delays of $(v_2,v_3)$ and $(v_3,v_2)$ physical paths
denoted by $y$. 
%%
If $y=z-x\pm\varepsilon$, the sequence $v_2-v_1-v_3$ is mismatched and should
be adjusted to $v_1-v_2-v_3$ by deleting edge $(v_1,v_3)$ and 
then adding a new $(v_2,v_3)$. 
If $y=x-z\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and
should be adjusted to $v_1-v_3-v_2$ by deleting edge $(v_1,v_2)$ and adding a
new $(v_3,v_2)$. 
The  $\varepsilon$ is a small positive real number denoting
additional delays caused by possible forwarding and jitter delays. 
%%
The advantages of \emph{HAND} are that it
\begin{inparaenum}[\itshape i\upshape)]
  \item does not need any clock synchronization,
  \item is a fully distributed algorithm.
  \item involves low traffic overhead,
  \item can be used in dynamic \p\ environments, and 
  \item furnishes low query response times.
\end{inparaenum}
%
% TODO: SOME DISCUSSION
%
%Measurements conducted for evaluation purposes showed that in a static
% environment the algorithm can effectively decrease traffic cost by about 77
%percent and shorten the query response time by about 49 percent in less than
%two minutes. In a dynamic environment it shows similar behavior and with the
%size of the overlay network having little impact on the effectiveness of the
%algorithm. Compared to LTM both algorithms have almost the same traffic
%reduction rate, however on the response time reduction rate HAND has a higher
%one by about 4 percent. The traffic overhead of HAND is much less than that of
%LTM by an average of 55 percent.
In terms of the $3$ stated criteria, \emph{HAND} fares as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% similar traffic reduction rate savings to LTM
medium &
% The traffic overhead of HAND is much less than that of LTM by an average of
% 55 percent.
low &
% no clock syncing needed, fully distributed and with low control overhead the
% algorithm can be considered scalable.
high
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Adaptive Peer Selection (APS)}
The \emph{Adaptive Peer Selection (APS)} approach uses 
machine learning techniques to form peer selection strategies based on past
experience~\cite{BFLZ2003}. A decision tree is used to rate peers based on
information collected for the characteristics of established connections. Such
features include connection link load, bandwidth, and past uploading experience.
Subsequently, a Markov decision process is introduced as a mechanism to shape
the policy for switching among the peers. The success of approach depends on
how fast the introduced peer selection functions. Admittedly, \emph{APS} is slow 
due its on-line learning process and inherent complexity \cite{ZZLZ2009}. As far
as the $3$ criteria is concerned, \emph{APS} has as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% machine learning the best way to adapt the overlay 
high &
% high computation overhead for learning and very slow convergence speed for
% the learning process.
high &
% Complexity of computation, and slow convergence speed prevents the approach
% to scale, especially in high churn environments.
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \emph{Innocuous Topology Aware Overlay Construction (ITA)}
approach~\cite{PRFM2009} seeks to offer both an overlay formation approach and
an effective way to carry out searching. When constructing the overlay,
\emph{ITA} exploits the notion of \emph{short} and \emph{long} connections.
Should $N$ be the number of network peers,  $\alpha \leq 1 $ a system-wide magic
number and $x$ an $\alpha$-related latency threshold, the bootstrapping peer
randomly selects $\alpha \ast N$ ``close'' (latency below $x$) and 
$\left( 1 - \alpha \right) \ast N$ distant (latency above $x$) nodes
as its neighbors.
%%AD how do they select all these magic constants???
%%VM This α constant seems to be the percentage of close neighbours selected by
% a peer out of its total degree. Can't find the criterion with which it is
% chosen though. Maybe we can ask... Mema :)
Searching occurs in two phases: in the initial phase, the querying node
floods its distant neighborhood  with $TTL = 1$.
Subsequently, peers receiving a query over a ``long link'' commence a 
local flood with $TTL=ttl$ where \emph{ttl} is system-defined.
%%AD how are you supposed to define these params?? in a fixed manner??
%%
%% VM Don't understand... the paper says that for increased awareness we need a
%% small α (page 7). But in the begining they give that short links (close-by)
%% are given by α*Ν. I guess this gets smaller for smaller α.... Also on
%% page 7 they say they choose α to be 0.1, 0.05 and 0.033 and that
%% this equals to ``10, 20, 30 long and and the same number of short links''.
%% I don't understand how they deduce these numbers. Since short links is given
%% by α*Ν and long by (1-α)*Ν at least the numbers should be different from
%% short and long links...
The main objective of the overlay construction phase is to yield a network that
exhibits low clustering. In turn, this is a beneficial characteristic for
random graphs as it can lead to a larger coverage of peers and at the same time
help reduce duplication of messages travelling around the network. This
combination offers efficient lookups that pose minimal or no negative impact to
other mechanisms possibly employed by the \p\ systems (e.g., 1-hop replication
or dynamic querying mechanisms). Experimental results in the same paper suggest
a 50\% reduction in communication latency among peers by cutting off some 20\%
of the \emph{IP}-level traffic generated.
%%
\emph{ITA} places as follows in the context of the $3$ criteria:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% low clustering with larger coverage of peers with the same number of messages
% and reduced duplication.
medium &
% construction at peer join, while searching using local ``floods''
low &
% the selection of neighbors is done at join time. No overlay adaptation means
% low scalability in dynamic environments.
medium
\end{tabular}
}
\end{center}

>>>>

The key objective of the {\sl Gia} system~\cite{CRBLS2003} is 
to help alleviate the scalability omnipresent
in unstructured \p\ file-sharing systems.
At first, {\sl Gia} replaced {\sl Gnutella}'s blind flooding 
with random walks.
Although this adoption was 
a step in the right direction \cite{LCCLS2002},
issuing a single copy of the query within the network
effectively reduces the search scope and may negatively affect 
the success rate of the query in question.
To overcome this limitation, {\sl Gia} introduces
a token-based flow control mechanism 
that gradually redirects queries to nodes which are more
likely to answer. This flow control mechanism also helps prevent node
overloading as each peer ``announces'' the number of query requests it 
can handle, in terms of tokens, to its neighbors; to this end, 
peers only forward query requests to nodes that they previously
received tokens from. Further refinement to the search mechanism is the
support for \emph{one--hop replication} of pointers to content.
{\sl Gia} also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc., of \p\ nodes and uses this
information when connecting nodes to each other.
By using a topology adaptation algorithm, 
{\sl Gia} places low capacity nodes within 
short proximity to peers with high performance features.
This topology adaptation algorithm is based on the metric 
each node maintains about its satisfaction --ranging between $0$ and $1$--
for the neighbors it finds itself associated with. 
Through message exchange, a peer can establish new connections 
or drop superseded ones in order to improve its satisfaction.
Despite the fact that {\sl Gia}'s topology adaptation algorithm 
that primarily focuses on the satisfaction of peers improves the network's 
scalability it falls short in addressing the mismatch problem
as considerations for the underlying network are not handled in explicit
terms \cite{LXLNZ2005}. Moreover it reduces the search scope, exhibits poor
performance in the worst case when matching data is not found quickly
\cite{PR2004,HJ2004} and can potentially build  disconnected topologies
\cite{MBL2006}.
%
In terms of the $3$ stated criteria, {\sl Gia}'s approach is as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Reduces the search scope.
medium &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
Another problem with topology unaware
systems is the duplication of messages due to cycles in the network graph.
Interestingly, such cycles appear even along the correct forwarding path.
\cite{ZKB2008} focuses on this exact deficiency of overlay networks and
introduces the \emph{Distributed Cycle Minimization Protocol
(DCMP)}, a dynamic, fully distributed method that removes cycles;
this is accomplished without sacrificing
overlay connectivity, resilience and other key properties of unstructured
\p\ architectures and by avoiding a hierarchical organization of peers. 
Once a cycle is detected in {\it DCMP}, the most powerful node in that cycle 
is elected as the \emph{Gate Peer} and the cycle is then broken in that place
that it will result in the minimization of the distance between the
\emph{Gate Peer} and all other nodes that are currently part of the cycle. 
This process is managed by using two specialized message types 
namely, \emph{Information Collection Message (ICM)} and \emph{Cut Message (CM)}. 
\emph{DCMP} bases its operation on messages whose travel is limited by an
imposed \emph{TTL} value (max set to $7$ for most cases). This inherently limits
the protocol in detecting cycles that span for more than \emph{TTL} nodes.
Even though cycle elimination does improve network performance, 
it cannot  directly contribute to the solution of the topology mismatch
problem, while its performance in a high traffic and churn environments and its
ability to retain important characteristics of a {\sl Gnutella}-like topology (i.e.,
like degree distribution, average peer distance, diameter e.t.c.) has been
doubted~\cite{CSG2010}. 
On the other hand, even though some of the overhead
saved by the duplicate message reduction is spent to control the cycle cutting
mechanism it is reported that still stays for example one to two orders of
magnitude less than LTM due to its ``lazy'' broadcasting of control messages
(as opposed to LTM's periodic approach) \cite{ZKB2008}.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
% TODO: SOME DISCUSSION
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
The expected \emph{DCMP} behavior as far as our $3$ criteria is:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It returns more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimizes this as possible.
low &
% fully distributed method
high
\end{tabular}
}
\end{center}

@@

In \cite{LCCLS2002}, a \emph{k-walker} query algorithm is presented and shown
that using it along side square-root allocation results in performance similar to
{\sl Gnutella}'s query flooding method but incurring up to two
orders of magnitude less network traffic. Also checks $3$ strategies for
replica placement, namely \emph{owner replication} where an object is replicated
at the requesting node, \emph{path replication} that caches the object along the
path from the requesting to the providing node and \emph{random replication}
where the replication is taking place randomly on visited nodes. Observations in
this work are not directly applicable to structured DHTs, because it is assumed
that the lookup time for an object depends only on the number of replicas and
not the placement strategy \cite{RS2004}.

@@

%In \emph{Adaptive Connection Establishment (ACE)} \cite{LZXN2004}, the
%authors extend the idea of AOTO by introducing optimizations based on the
%depths of the minimum spanning trees. But since the network delay is not
%always a reliable estimation method to detect the physical location of peers,
%the algorithm still suffers from the discrepancies caused by mis-located nodes.
%%
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% compared to LTM it has slow convergence speed because of the information
% exchange among each peer and all its neighbors.
medium &
% A little bit better that AOTO since the computation here is done within a
% certain diameter from the source peer
medium &
% Larger diameter topologies lead to better topology optimization
% rate but also to higher communication and computation overhead.
medium
\end{tabular}
}
\end{center}

@@

The \emph{piggybacking component} requires peers 
to probe immediate neighbors using delay distance measurements 
and store this information locally. 
The algorithm introduces a special query message type, 
the \emph{Piggy Message (PM)} which includes information about 
the neighbor identification (\emph{IP}) and measured distance ($d$). PMs are
piggybacked to normal
{\sl Gnutella} messages. 
When a node $P$ receives a query from $Q$, it constructs a
$PM_{PQ}$, piggybacks it to the query and forwards it to $P$'s neighbors. 
As soon as a neighbor detaches a received $PM_{PQ}$, records the distance 
$d_{PQ}$ and processes the query.
% When the neighbors receive it they detach the $PM_{PQ}$, 
% record the distance $d_{PQ}$ and process the query normaly. 
Selection of which incoming queries
should be piggybacked with a \emph{PM} is determined using either a
% proposed by either
\emph{pure probability-based (PPB)} or a \emph{new neighbor triggered (NNT)}
policy.

The \emph{neighbor comparison and selection} component defines that a peer $S$
probe all his $2$-hops away neighbors (a set denoted as $ N^2(S)$) not probed
thus far. Let $P$ be a $1$-hop distance neighbor of $S$, and $Q$ be a probed
peer by $S$. When $S$ receives a message piggybacked with message $PM_{PQ}$, 
% we identify the following cases.  %%AD put it passive as below.. 
the following $2$ cases are identified:

\begin{enumerate}
  \item If $Q$ is already a direct neighbor of $S$ then we check 
	the distances $d_{SQ}$, $d_{SP}$ and $d_{PQ}$. 
	If either $d_{SQ}$ or $d_{SP}$ is the longest, then the longest
  	link will be placed in a \emph{will-cut} list\footnote{A peer will not send or
  	forward queries to connections in its will-cut list but will preserve them
  	for some time in order not to effect ongoing response messages travelling the
  	inverse path.}. 
	If $d_{PQ}$ is the longest, then nothing is done by $S$; being
  	fully distributed, neighbor comparison and selection process, will have the
  	opportunity to handle $PQ$ link when initiated by peers $P$ or $Q$.

  \item If $Q$ is strictly a $2$-hop neighbor of $S$ and have never probed $Q$
  	in the past, stores distance $d_{SQ}$ and checks 
	distances $d_{SQ}$, $d_{SP}$ and $d_{PQ}$.
  	If $d_{SQ}$ is the longest, $S$ will not create link $SQ$. If $d_{SP}$ is the
  	longest, $SQ$ will be created and $SP$ will be put into the will-cut list.
  	If $PQ$ is the longest, links $SP$ and $SQ$ will be preserved expecting that
  	$P$ or $Q$ will disconnect $PQ$ later.
\end{enumerate}

@@

As discussed above, \emph{THANCS} is fully distributed and needs only minimum knowledge
of, at most, a $2$-hop distant peers. This features renders 
the method a good candidate for large overlay networks. 
Also its topology adaptation helps construct a well fit overlay
with respect to the underlying network--at least with respect to network
distances. In addition, will-cut list and distance caches (which store already
probed peers) minimize the unnecessary messages for the network maintenance.
%%
In \cite{HLY2010}, the simulation-derived results of \emph{THANCS} as far
average broadcast delay and overlay improvement guarantees are discussed;
overall, \emph{THANCS} fares as follows regarding the $3$ stated criteria:
%%AD rephrased more diplomatically the following as above.. 
% There are works in the literature though that criticize, through simulation
% results, the algorithm's average broadcast delay and overlay improvement
% guarantee \cite{HLY2010}.
% These characteristics are depicted to the $3$ evaluation criteria we use in this
% survey as follows:
%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% 
medium &
% trivial overhead compared to the query cost savings and its convergent speed
% is faster than minimum spanning tree approaches so less overall overhead cost.
low &
% completely distributed and needs no global knowledge,
high
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \emph{Hops Adaptive Neighbor Discovery (HAND)} algorithm~\cite{CLZHC2006}
uses a fully-distributed triple--hop adjustment strategy, applied to a network
graph $G$ in order to create an optimal graph $G^{*}$, free of the implications
of topology mismatch. This optimality is attained if all peer hop 
sequences $(v_1, v_2, \ldots, v_k)$ of $G$ exist in $G^{*}$ and are in the same
order. The latter indicates that in practice triple sequences $(v_1, v_2, v_3)$
are used. A mismatch is detected as follows: should we want to verify
a sequence, say $v_2-v_1-v_3$, two probing messages are dispatched from $v_1$ to
$v_2$ and $v_3$ and yield delays of $x$ and $z$ respectively.
%
When the probing message arrives at $v_2$, it gets forwarded
directly to $v_3$. 
Similarly, the message reaching $v_3$ is directly forwarded to $v_2$.
The above two forwarding actions seek to quantify 
the corresponding delays of $(v_2,v_3)$ and $(v_3,v_2)$ 
% physical paths denoted by $y$. 
for the physical path $y$.
%%AD check above... it is one path (not paths right?)
%%
If $y=z-x\pm\varepsilon$, the sequence $v_2-v_1-v_3$ is mismatched and should
be adjusted to $v_1-v_2-v_3$ by deleting edge $(v_1,v_3)$ and 
then adding a new $(v_2,v_3)$. 
If $y=x-z\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and
should be adjusted to $v_1-v_3-v_2$ by deleting edge $(v_1,v_2)$ and adding a
new $(v_3,v_2)$. 
The  $\varepsilon$ is a small positive real number denoting
additional delays caused by possible forwarding and jitter delays. 
%%
The advantages of \emph{HAND} are that it
\begin{inparaenum}[\itshape i\upshape)]
  \item does not need any clock synchronization,
  \item is a fully distributed algorithm.
  \item involves low traffic overhead,
  \item can be used in dynamic \p\ environments, and 
  \item furnishes low query response times.
\end{inparaenum}
%
% TODO: SOME DISCUSSION
%
%Measurements conducted for evaluation purposes showed that in a static
% environment the algorithm can effectively decrease traffic cost by about 77
%percent and shorten the query response time by about 49 percent in less than
%two minutes. In a dynamic environment it shows similar behavior and with the
%size of the overlay network having little impact on the effectiveness of the
%algorithm. Compared to LTM both algorithms have almost the same traffic
%reduction rate, however on the response time reduction rate HAND has a higher
%one by about 4 percent. The traffic overhead of HAND is much less than that of
%LTM by an average of 55 percent.
In terms of the $3$ stated criteria, \emph{HAND} fares as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% similar traffic reduction rate savings to LTM
medium &
% The traffic overhead of HAND is much less than that of LTM by an average of
% 55 percent.
low &
% no clock syncing needed, fully distributed and with low control overhead the
% algorithm can be considered scalable.
high
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Adaptive Peer Selection (APS)}
The \emph{Adaptive Peer Selection (APS)} approach uses 
machine learning techniques to form peer selection strategies based on past
experience~\cite{BFLZ2003}. A decision tree is used to rate peers based on
information collected for the characteristics of established connections. Such
features include connection link load, bandwidth, and past uploading experience.
Subsequently, a Markov decision process is used
% introduced as a mechanism 
to shape the policy for switching among the peers. The success of approach depends on
how fast the introduced peer selection functions. Admittedly, \emph{APS} is slow 
due its on-line learning process and inherent complexity \cite{ZZLZ2009}. 
\emph{APS}' behavior regarding the $3$ criteria has as follows:
% As far as the $3$ criteria is concerned, \emph{APS} has as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% machine learning the best way to adapt the overlay 
high &
% high computation overhead for learning and very slow convergence speed for
% the learning process.
high &
% Complexity of computation, and slow convergence speed prevents the approach
% to scale, especially in high churn environments.
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \emph{Innocuous Topology Aware Overlay Construction (ITA)}
approach~\cite{PRFM2009} seeks to offer both an overlay formation approach and
an effective way to carry out searching. When constructing the overlay,
\emph{ITA} exploits the notion of \emph{short} and \emph{long} connections.
Should $N$ be the number of network peers,  $\alpha \leq 1 $ a system-wide magic
number and $x$ an $\alpha$-related latency threshold, the bootstrapping peer
randomly selects $\alpha \ast N$ ``close'' (latency below $x$) and 
$\left( 1 - \alpha \right) \ast N$ distant (latency above $x$) nodes
as its neighbors.
%%QUE how do they select all these magic constants???
%%ANS This α constant seems to be the percentage of close neighbors selected by
% a peer out of its total degree. Can't find the criterion with which it is
% chosen though. Maybe we can ask... Mema :)
Searching occurs in $2$ phases: in the initial, the querying node
floods its distant neighborhood  with \emph{TTL=1}.
Subsequently, peers receiving a query over a ``long link'' commence a 
local flood with \emph{TTL=ttl} where \emph{ttl} is system-defined.
%%QUE how are you supposed to define these parameters?? in a fixed manner??
%%
%%ANS Don't understand... the paper says that for increased awareness we need a
%% small α (page 7). But in the beginning they give that short links (close-by)
%% are given by α*Ν. I guess this gets smaller for smaller α.... Also on
%% page 7 they say they choose α to be 0.1, 0.05 and 0.033 and that
%% this equals to ``10, 20, 30 long and and the same number of short links''.
%% I don't understand how they deduce these numbers. Since short links is given
%% by α*Ν and long by (1-α)*Ν at least the numbers should be different from
%% short and long links...
The main objective of the overlay construction phase is to yield a network that
exhibits low clustering. In turn, this is a beneficial characteristic for
random graphs as it can lead to a larger coverage of peers and at the same time
help reduce duplication of messages travelling around the network. This
combination offers efficient lookups that pose minimal or no negative impact to
other mechanisms possibly employed by the \p\ systems (e.g., $1$-hop replication
or dynamic querying mechanisms). Experimental results in the same paper suggest
a $50$\% reduction in communication latency among peers by cutting off some $20$\%
of the \emph{IP}-level traffic generated.
%%
Regarding the $3$ criteria, \emph{ITA} is placed as follows:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% low clustering with larger coverage of peers with the same number of messages
% and reduced duplication.
medium &
% construction at peer join, while searching using local ``floods''
low &
% the selection of neighbors is done at join time. No overlay adaptation means
% low scalability in dynamic environments.
medium
\end{tabular}
}
\end{center}
